\bf Probabilistic Forecasts in Hierarchical~Time~Series

### 2020-01-27 R1/Response.tex

		\textit{When the empirical evaluation is focused on bias, then it would make sense to include an error that measures bias in addition to the squared error.}\\

		We now also report the total error for all methods to highlight bias.  Here we see that bias correction method 1 removes bias, while bias correction method 2 in fact worsens bias.  A new insight that we are able to make is to recognise that reconciliation without bias correction can mitigate bias.  For example, even if bias correction is not used at all, OLS reconciliation significantly reduces bias for both the log transformation and Box Cox transformation.  This is likely to occur since bias lies in a direction that is almost orthogonal to the coherent subspace.\\

		\textit{Moreover, simply showing the MSE without any confidence intervals or measures of significance is not sufficient for the reader to assess the results.  It would also be useful to show the MSE relative to the base forecasts or the percentage improvement that is obtained.} \\

		We now report all results relative to the base forecasts. We also have added stars to the tables that report our results to indicate when a method significantly upon base forecasts.\\

@@

	    \textit{The best performing reconciliation method is MinT with shrinkage, but the authors never state	the value of the shrinkage parameter or how it was chosen.  Similarly, they compare with variance scaling without explaining what they mean by variance scaling.}\\

	    The shrinkage estimator is that of Sch\"afer and Strimmer~(2005). Details on this method (including the choice of shrinkage parameter) are now provided.  Similarly, we now provide more detail on variance scaling, which simply refers to using the variance of one step ahead in-sample forecast errors.\\

	    \textit{In addition to the above mentioned shortcomings, I think the authors should reconsider their empirical evaluation. Maybe a second case study or a simulation study is needed to show the value of the geometric insights provided. We already know that MinT is better than OLS and WLS. What is the new and better reconciliation approach that has come from the geometric insights?}\\

		The objective of this paper is not to propose a new and better reconciliation approach but to establish new results that lead to clearer understanding of the properties of existing methods that in turn motivate research into new methods.  Therefore, while the paper does not include a new method, it does provide insights into how new methods should (or should not) be developed.  For examples of this, see the discussion on page 19 just before Section 4.1 and comments in the conclusion.\\

@@

		In this paper, the purpose of the empirical evaluation is to provide a demonstration of the theoretical results that we have established.  We agree that this could be improved.  We have greatly expanded Section 5.2 to more clearly investigate two different loss functions and demonstrate two different understandings of optimality.\\

		Improving the existing empirical application in the ways suggested by the referee has lengthened the paper considerably.  Therefore, we prefer to refrain from including a second empirical demonstration.\\

		\item \textit{Improvement guarantees: The boxplot in Figure 8 shows that OLS always improves MSE, while this is not the case for the other reconciliation approaches. To gain a better understanding of the implications of Theorem 3.2, it would be useful to show that the other approaches always
		improve accuracy in their transformed spaces.}\\

	    We now expand section 5.2 to report results for two different error metrics.  Furthermore we have added additional insights in Section 3.4 that are now also demonstrated in this section.  In particular we show that while the distance reducing property of Theorem 3.2 depends entirely on the choice of loss function, minimising the expected loss function can always be achieved by a MinT approach.\\

### 2020-01-27 R1/Letter.tex
minor changes to letter

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item We have greatly expanded the empirical study including more measures of forecast accuracy (including those specifically measuring bias).  This has led to the insight that reconciliation alone can in fact reduce the bias of an estimator.  Where differences in forecast accuracy are significant.
	\item We introduce some new results about MinT that make it clear that MinT minimises expected loss for a wider range of loss functions than previously thought.
	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negativity, 
\end{enumerate}

>>>>

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item We have greatly expanded the empirical study including more measures of forecast accuracy (including those specifically measuring bias).  This has led to the insight that reconciliation alone can in fact reduce the bias of an estimator.  We also now also report where differences in forecast accuracy are statistically significant.
	\item We introduce some new results about MinT that explicitly makes the connection between trace minimisation and minimises a loss function based on Euclidean distance.  We also prove a new result that MinT minimises expected loss for loss functions based on generalised Euclidean distance.  This result is demonstrated in an expanded empirical application in section 5.2 that includes a wider range of loss functions. 
	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negative forecasts, and state-space models. 
\end{enumerate}
